Walling up Backdoors in Intrusion Detection Systems

### 2019-10-15 paper/paper.tex
Change title
Reviewer corrections

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Bricking up backdoors in Intrusion Detection Systems}

@@

If we denote by $\boldsymbol X \in \mathbb R ^n$ a random vector drawn from the feature space and by $f(\boldsymbol X) \in [0,1]$ the  prediction function, the \gls{pdp} for the $i$th feature $X_i$ can be expressed as
\begin{equation}
\text{PDP}_i(w) = \mathbb E_{\boldsymbol X}\Big(f(X_1,\ldots,X_{i-1},w,X_{i+1},\ldots X_n)\Big) . % \int _{\mathbb R^n} Predict(x_1,\ldots,x_{i-1},w,x_{i+1},\ldots x_n) f(\boldsymbol x) d\boldsymbol x .
\end{equation}
Empirically, we can approximate the distribution of the feature space using the distribution of observed samples. Hence, at a given point $w,$ the \gls{pdp} can be found by setting the corresponding value of all samples in the dataset to $w$ and averaging over the predictions of the resulting modified dataset.

\subsubsection{Accumulated Local Effects}
Due to feature dependence it is very likely that areas exist in the feature space which are very unlikely
% have a very low probability
to occur. Since a model is trained with real, observed data, the training set therefore does not include samples for these areas, which causes the model's predictions to become indeterminate for these areas, %. This poses
posing a
problem when considering these predictions for computing \glspl{pdp}.

>>>>

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Walling up Backdoors in Intrusion Detection Systems}

@@

If we denote by $\boldsymbol X \in \mathbb R ^n$ a random vector drawn from the feature space and by $f(\boldsymbol X) \in [0,1]$ the  prediction function, the \gls{pdp} for the $i$th feature $X_i$ can be expressed as
\begin{equation}
\text{PDP}_i(w) = \mathbb E_{\boldsymbol X}\Big(f(X_1,\ldots,X_{i-1},w,X_{i+1},\ldots X_n)\Big) . % \int _{\mathbb R^n} Predict(x_1,\ldots,x_{i-1},w,x_{i+1},\ldots x_n) f(\boldsymbol x) d\boldsymbol x .
\end{equation}
Empirically, we can approximate the distribution of the feature space using the distribution of observed samples. Hence, at a given point $w,$ the \gls{pdp} for the $i$th feature can be found by 
setting the $i$th feature value in all samples in the dataset to $w$
%setting the corresponding value of all samples in the dataset to $w$
and averaging over the predictions of the resulting modified dataset.

\subsubsection{Accumulated Local Effects}
In real situations, datasets usually exhibit a non-negligible degree of feature dependence. 
Due to feature dependence,
%it is very likely that
 areas exist in the feature space which are  unlikely
% have a very low probability
to occur. Since a model is trained with real, observed data, the training set therefore might not include samples for these areas.
% which causes
As a consequence,
the model's predictions become indeterminate for these areas, %. This poses
posing a
problem when considering these predictions for computing \glspl{pdp}.
